Effects of the body force on the pedestrian and evacuation dynamics

### 2020-02-06 paper.tex
correccion de gramatica chica
reemplace los 1.2E4 por 2.6E4

Fig.~\ref{vd_vs_te}  shows either FIS or FIF, and a FIS+FIF pattern
for desired velocities $v_d>1.2\,$m/s. The 
evacuation time attains a FIS+FIF pattern for compression coefficients below 
$k=1.2\,$E5. This means that ``soft'' individuals can attain this 
behavioral pattern.  Notice that higher values of $k_n$ allow 
only FIS or FIF patterns. For the highest explored value $k_n=1.2\,$E6, no 
FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
= 1.2\,$E4 are very similar since the body force intensity is of the same order
or less than the social 
force for these stiffness values. \\

Despite the presence of the FIS or FIF pattern, the evacuation time at a 
fixed value of $v_d$ decreases for increasing values of $k_n$ (whiting the examined interval). 
This means that stiffer pedestrians evacuate faster than soft pedestrians. 
To further investigate this 
phenomenon, we computed the mean velocity of the whole crowd as a function of the 
stiffness $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the actual mean velocity in the 
$x-$direction as a function of the stiffness $k_n$ for three different desired 
velocities. In all cases, the velocity increases with the stiffness. From 
$k_n=0$ to $k_n=1.2\,$E4 the increment of velocity is not as significative as it 
is for higher $k_n$. \\

@@

We computed the contact network in the same way in the bottleneck geometry. Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values (see caption for details). The degree is zero because the pedestrians do not touch each other. When the density reaches 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density continuous increasing, the mean degree increases towards the asymptotic degree six. Degree six corresponds to the maximum packing density for identical hard circles.\\

@@

The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry. Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels. $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry. There is little to no change in the speed from zero to $k_n=$1.2~E4, from this value on, the diminishing of velocity is more abrupt.\\

>>>>

Fig.~\ref{vd_vs_te}  shows either FIS or FIF, and a FIS+FIF pattern
for desired velocities $v_d>1.2\,$m/s. The 
evacuation time attains a FIS+FIF pattern for compression coefficients below 
$k=1.2\,$E5. This means that ``soft'' individuals can attain this 
behavioral pattern.  Notice that higher values of $k_n$ allow 
only FIS or FIF patterns. For the highest explored value $k_n=1.2\,$E6, no 
FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
= 2.6\,$E4 are very similar since the body force intensity is of the same order
or less than the social 
force for these stiffness values. \\

Despite the presence of the FIS or FIF pattern, the evacuation time at a 
fixed value of $v_d$ decreases for increasing values of $k_n$ (whiting the examined interval). 
This means that stiffer pedestrians evacuate faster than soft pedestrians. 
To further investigate this 
phenomenon, we computed the mean velocity of the whole crowd as a function of the 
stiffness $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the actual mean velocity in the 
$x-$direction as a function of the stiffness $k_n$ for three different desired 
velocities. In all cases, the velocity increases with the stiffness. From 
$k_n=0$ to $k_n=2.6\,$E4 the increment of velocity is not as significative as it 
is for higher $k_n$. \\

@@

We computed the contact network in the same way as in the bottleneck geometry. Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values (see caption for details). The degree is zero when the pedestrians do not touch each other. When the density reaches 4.5, a few pedestrians start to touch each other increasing the mean degree. As the density continuous increasing, the mean degree increases towards the asymptotic degree six. Degree six corresponds to the maximum packing density for identical hard circles.\\

@@

The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry. Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels. $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry. There is little to no change in the speed from zero to $k_n=$2.6~E4, from this value on, the diminishing of velocity is more abrupt.\\
